The Slowdown of TFP \\ Exogenous and Endogenous Mechanisms

### 2017-12-10 Latex/MacroLunch_Dec2017/macrolunch_dec2017.tex
added figures from the new nice specification and FEV-table, and also added FEVs in the presentation

    \hspace{2.25cm}
\begin{large}
	\begin{tabular}{lccc}
	\hline
		& News & IT & Total \\
		\hline
	TFP	           & 0.4081  & 0.4026 & 0.8107  \\
		\hline
	\end{tabular}
\end{large}

@@

@@

\item Shares of FEV of TFP explained ...
	\begin{itemize}
	\item ... are also in line with the Barsky \& Sims result ...
	\item [] For BS, news explains around 45\%, compared to 37\% here

	\item ... yet suggest that the IT shock plays an important role as well
	\end{itemize}

>>>>

    \hspace{2.25cm}
\begin{large}
	\begin{tabular}{lccc}
	\hline
		& News & IT & Total \\
		\hline
	TFP	           & 0.20384  & 0.52596 & 0.72981  \\
		\hline
	\end{tabular}
\end{large}

@@

	\vspace{0.1cm}

@@

\item Shares of FEV of TFP explained ...
	\begin{itemize}
	\item ... are also in line with the Barsky \& Sims result ...
	\item [] For BS, news explains around 45\%, compared to 20\% here

	\vspace{0.1cm}

	\item ... yet suggest that the IT shock plays an important role as well (around 52\%)

	\vspace{0.1cm}

	\item ... and indeed the IT shock \emph{complements} the news shock, instead of substituting for it
	\item [] For BS, the single identified shock explains around 45\%, while our two identified shocks explain around 73\%
	\end{itemize}
